---
title: "p8105_hw1_zz2603"
author: "Ziyi Zhao"
date: "9/16/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)

```


```{r problem 1, echo=TRUE}
set.seed(100)

## set four variables in data frame
rand_norm <- rnorm(8)
log_vec <- rand_norm>0
char_vec <- c("husky","Akita","Shiba Inu","Alaska","Samoyed","Pekingese",
              "British Blue Cat","Orange Cat")
level_vec <- c("Low","High","High","Low","Low","Mid","Mid","Mid")%>%factor()

## combine them together and create a new data frame
prob1_df <- tibble(rand_norm,log_vec,char_vec,level_vec)
prob1_df

## see mean of four variable
mean(pull(prob1_df,rand_norm)) ## it works!
mean(pull(prob1_df,log_vec)) ## it also works!
mean(pull(prob1_df,char_vec)) ## it does not work and returns NA
mean(pull(prob1_df,level_vec)) ## it does not work and returns NA
```
Only mean of numeric and logical vectors return the numeric result.
However, the other two vector, in character and factor, return NA.

```{r problem 1 convert type, echo=True}
log_num <- as.numeric(log_vec)
log_num
char_num <- as.numeric(char_vec)
char_num
fac_num <- as.numeric(level_vec)
fac_num
```
As we transfer logical vector into numeric vector, all values ("True" and "False") are tranferred to 1 and 0. This is why we get numeric value when we apply mean function to logical vector.
All values in character vector are transferred into NA when we tried to convert non-numeric character into numeric values. This is why mean function return NA.
When we converted the factor vector into numeric value, three levels are converted into numeric values 1,2 and 3. However, mean of factor vector return NA. I think the reason is that all values in factor vector are non-numeric.

```{r,echo=TRUE}
## in last chunk, we convert log_vec into numeric vector log_num
logNumRD <- log_num*rand_norm 
logNumRD
logFacRD <- as.factor(log_vec)*rand_norm ## multiplying seems quite useless
logFacRD
logFacNumRD <- (as.factor(log_vec)%>%as.numeric())*rand_norm
logFacNumRD
```

```{r problem 2,echo=TRUE}
x <- rnorm(500)
y <- rnorm(500)
logic_vtr <- (x+y)>1
logic_num <- as.numeric(logic_vtr)
logic_ftr <- as.factor(logic_vtr)

plot_df <- tibble(x,y,logic_vtr,logic_num,logic_ftr)
plot_df
```
* the size of dataset is `nrow(plot_df),ncol(plot_df)`.
* the mean, median and standard deviation are `mean(pull(plot_df,x)), median(pull(plot_df,x)), sd(pull(plot_df,x))`. 
* the proportion of cases for logical vector is `sum(pull(plot_df,logic_vtr))/length(pull(plot_df,logic_vtr))`.

```{r }

```

